rbeast2: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-22 article.tex
Process feedback, thanks @rsetienne

However, BEAUti cannot be called from a command-line script.
This implies that when the user 
wants to explore the consequences of various settings, this must be done manually.
This is the common workflow when using a few alignments and doing a superficial 
analysis of sensitivity of the reconstructed tree to model settings. 
For exploring many trees (for instance from simulations) and for
more thorough sensitivity analysis, one would like to loop through 
multiple (simulated) alignments, nucleotide substitution models, 
clock models and tree priors. 
One such tool to replace BEAUti is \verb;BEASTmasteR; \cite{beastmaster},
which focuses on morphological traits and tip-dating, but also 
supports DNA data. \verb;BEASTmasteR;, however, takes hundreds of
lines to set up (next to a Miscrosft Excel spreadsheet), 
resulting in only 7 citations, all before 2017.

@@

However, for exploring the output of many BEAST2 runs, 
one would like a script to collect all parameters' ESSes,
parameter traces and posterior phylogenies.
There is no single package that offers a complete solution,
but examples of R packages that offer a partial solution
are \verb;rBEAST; \cite{rBEAST_ratmann} and 
\verb;RBeast; \cite{RBeast_faria}.

@@

\verb;rbeast2; is the first R package that unifies the
full workflow of working with BEAST2. 
Whilst \verb;BEASTmasteR; needs hundreds of lines to create
a BEAST2 configuration file, with \verb;rbeast2; the same 
can be created by a simple one-liner. Unlike \verb;rBEAST; 
and \verb;RBeast;, \verb;rbeast2; implements all of Tracer's
primary functionality. This makes \verb;rbeast2; a complete 
solution for using BEAST2 from R.

>>>>

However, BEAUti cannot be called from a command-line script.
This implies that when the user 
wants to explore the consequences of various settings, this must be done manually.
This is the common workflow when using a few alignments and doing a superficial 
analysis of sensitivity of the reconstructed tree to model settings. 
For exploring many trees (for instance from simulations) and for
more thorough sensitivity analysis, one would like to loop through 
multiple (simulated) alignments, nucleotide substitution models, 
clock models and tree priors. 
One such tool to replace BEAUti is \verb;BEASTmasteR; \cite{beastmaster},
which focuses on morphological traits and tip-dating, but also 
supports DNA data. \verb;BEASTmasteR;, however, takes hundreds of
lines to R code and a Miscrosft Excel file.

@@

However, for exploring the output of many BEAST2 runs, 
one would like a script to collect all parameters' ESSes,
parameter traces and posterior phylogenies.
There is no single package that offers a complete solution,
but examples of R packages that offer a partial solution
are \verb;BEASTmasteR;, \verb;rBEAST; 
\cite{rBEAST_ratmann} and 
\verb;RBeast; \cite{RBeast_faria}.

@@

\verb;rbeast2; is the first R package that unifies the
full workflow of working with BEAST2. 
Whilst \verb;BEASTmasteR; needs hundreds of lines to create
a BEAST2 configuration file, with \verb;rbeast2; the same 
can be created by a simple one-liner. Unlike \verb;BEASTmasteR;,
\verb;rBEAST; and \verb;RBeast;, \verb;rbeast2; implements all of Tracer's
primary functionality. There exists no package that calls BEAST2 from R.
\verb;rbeast2; sets up BEAST2, runs it, and analyzes its
results, making it a complete solution for using BEAST2 from R.
